%!TEX program = xelatex
% Resume of Arnav Sharma built using ModernCV
%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'


\usepackage[scale=0.83]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your nam
% \usepackage{fontspec}
% \usepackage{fontawesome}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Arnav} % Your first name
\familyname{Sharma} % Your last name
\title{R\'esum\'e}
% All information in this block is optional, comment out any lines you don't need
%\title{Roll No : 201125093}
% \extrainfo{331 Old Boys Hostel IIIT-Hyderabad}
% \address{201125093}{}
% \address{331 Old Boys Hostel }{IIIT-Hyderabad}

\phone[mobile]{(+91) 9701518597}
% \fax{201125093}
\email{arnavsharma93@gmail.com}

\homepage{researchweb.iiit.ac.in/\textasciitilde arnav.s}

\social[github]{arnavsharma93}

\social[linkedin]{arnavsharma93}
% The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------
\begin{document}


\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\vspace{-12mm} % reduce the vertical space so that the resume fits
% \section{Fields of Interest}
% % \cvitem{}{
% % \begin{itemize}
% \cvlistitem {Speech and Natural Language Processing}
% \cvlistitem {Web Development}
% \cvlistitem {*nix }
% \end{itemize}
% }
\section{Objective}
To spend my days designing systems and solving interesting puzzles with talented teammates.


\section{Summary}
Able to blend computer science education, software engineering experience, and communication skills to build elegant, reliable, maintainable systems


\section{Education}

\cventry{2011--2016}{B. Tech. (Hons) in Computer Science and MS in Computational Linguistics}{International Institute of Information Technology, Hyderabad}{}{}{ {\bfseries  CGPA--7.8}}  % Arguments not required can be left empty

\cventry{2011}{High School Certificate Examination}{Delhi Public School, Jalandhar}{}  {} { {\bfseries Percentage -- 91\%}}

\cventry{2009}{Senior School Certificate Examination}{Army Public School, Jalandhar}{}  {} { {\bfseries Percentage -- 92\%}}


\section{Work Experience}

\subsection{\bfseries{Software Developer}}

\cvitem{\textsc{Google Summer of Code - SSF}} {\hfill May'14--August'14}
\cvitem {}{Developed a testing framework - \href{http://eden.sahanafoundation.org/wiki/DeveloperGuidelines/Testing/EdenTest}{EdenTest} - built on Robot Framework for the open source organization Sahana's product \textit{Eden}. The project has reduced the number of bugs per code ratio to almost half and is used exensively in ATDD of Eden. It was mentored by \href{https://github.com/nursix}{\underline{Dominic Koenig}}.}

\cvitem{\textsc{AidIQ}} {\hfill September'14--Present}
\cvitem {}{I am working on building Continuous Integration solutions for Eden. This involves the following:
\begin{itemize}
    \item Ability to run Sahana Eden unit tests on GitHub Pull Requests for a specific branch (\href{https://travis-ci.org/flavour/eden}{\underline{here}}).
    \item Ability to run Sahana Eden functional tests (EdenTest) on a GitHub branch on demand.
    \item Ability to schedule and run Sahana Eden smoke tests (EdenTest) on a GitHub branch (nightly builds).
\end{itemize}
}

\cvitem{\textsc{Synapz Adaptive Technologies}} {\hfill June--September'13}
\cvitem {}{Worked as a full stack web developer where I developed an \textit{online judge for automatic evaluation codes}. Later, deployed it on \textit{Amazon Web Services}.}


\subsection{\bfseries{Research Assistant}}

\cvitem{\textsc{Language Technology Resource Center}} {\hfill May--Sept'13}
\cvitem {}{Engineered the website for \href{http://ltrc.iiit.ac.in/icon/2013}{\underline{{\bfseries International Conference On NLP-13}}}.}


\subsection{\bfseries{Teaching \& Mentoring}}

\cvitem{\textsc{Google Code-In}} {\hfill November--January'13, 14}
\cvitem {}{Appointed as a Google Code-In mentor for \textit{Sahana Software Foundation} where I mentored high school students in their introductory steps in Open Source contribution.}

\cvitem{\textsc{Teaching Assistant }} {\hfill August--December'13}
\cvitem {}{ Appointed as a teaching assistant at IIIT-Hyderabad for:
\begin{itemize}
    \item{Computer Networks} under \href{http://iiit.ac.in/people/faculty/faculty/shatrunjay.rawat} {\underline{Prof. Shatrunjay Rawat}}
    \item{ITWS} under \href{http://iiit.ac.in/people/faculty/vikram}{\underline{Dr. Vikram Pudi}} at IIIT-Hyderabad.
\end{itemize}}


\section{\bfseries{Projects}}

\subsection{\bfseries{Analysis of error propagation LTRC Parsing Pipeline}}
\cvitem{Mentor}{\href{http://www.iiit.ac.in/people/faculty/dipti}{\underline{{Prof. Dipti Misra Sharma}}}}
\cvitem{Description}{Analyzing the error propagation in the Parsing Pipeline for Hindi and improving the accuracy of the pipeline by remodeling it.}

\subsection{\bfseries{Twitter entity linking with Wikipedia}}
\cvitem{Mentor}{\href{http://iiit.ac.in/people/faculty/vv}{\underline{{Prof. Vasudeva Varma}}}}
\cvitem{Description}{Built a system which for a given tweet, finds the entities and then using contextual information about these entities, tries to link it with their corresponding Wikipedia page. Link to the {\href{https://www.dropbox.com/s/vw999ugx4bkh0ps/FinalVersion.mov} {\underline{video}} explaining the approach and working.}}

\subsection{\bfseries{Urdu to Hindi Transliterater}}
\cvitem{Mentor}{{\bfseries Dr. Riyaz Bhatt}}
\cvitem{Description}{Built a transliterater using tools such as GIZA++ and CRF Classifier which transliterates from Urdu to Hindi. It has an accuracy of 98.4.}

\subsection{\bfseries{Search Engine for Wikipedia}}
\cvitem{Mentors}{\href{http://www.iiit.ac.in/people/faculty/vv}{\underline{{Dr. Vasudeva Varma IIIT-H}}}}
\cvitem{Description}{Designed a fully functional offline Search Engine for Wikipedia in Python. Implemented the search engine on a 42 GB dump of Wikipedia. Search engine was built from scratch, starting from design to coding without using any helper library functions.}


\section{Minor Projects}

\begin{itemize}

\item {\bfseries Face recognizer}: As a course project of Statistical Methods of Artificial Intelligence, created a face recognizer by implementing Eigen Faces and using SVM.
\item {\bfseries Bash-like Shell}: A basic shell/terminal to simulate the a subset of the functionality provided by Bash.
\item {\bfseries Compiler for Decaf}: Built a compiler (front end to IR) for Decaf programming language.

\end{itemize}


\section{\bfseries{Technical Skills}}

\cvitem{Languages}{C, Python, Bash, PHP}
\cvitem{OS}{*nix}
\cvitem{Web} {HTML5, CSS, Javascript, Django, Bootstrap, Ruby on Rails,  Web2py}
\cvitem{Databases}{MySQL, SQLite3}
\cvitem{Miscellaneous}{Git, SVN, Apache, \LaTeX, Testing, Scikit-Learn}


\section{\bfseries{Achievements}}

\cvitem{Microsoft Code-Fun-Do}{Stood fourth in appathon organized by \textit{Microsoft India Development Center.}
}
\cvitem{ACM-ICPC Regionals}{Qualified for ACM-ICPC Amritapuri Regionals 2013.
}
\cvitem{AIEEE}{Secured \textit{All India Rank of 5195 (99.52 percentile)} in AIEEE 2011.
}
\cvitem{CBSE AISSCE}{Stood {\textit first} in science streams.
}
\cvitem{National Level Quizzing}{Participated in the quizzes such as \textit{Limca Records Quiz}.
}


\section{\bfseries{Interests}}

\cvlistitem{Quizzing}
\cvlistitem{Open Source Development}

\centerline{\small{{\bfseries Last updated} : \today.}}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

% \clearpage

% \recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
% \date{\today} % Letter date
% \opening{Dear Sir or Madam,} % Opening greeting
% \closing{Sincerely yours,} % Closing phrase
% \enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

% \makelettertitle % Print letter title

% \lipsum[1-3] % Dummy text

% \makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}
